### 2021-02-25 paper/fse21/eval.tex
Revised Figure 9.

\begin{figure}[t]
  \centering
  \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics[width=\linewidth]{img/precision}
    \vspace*{-1.5em}
    \label{fig:precision-fail}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Failed assertions of analysis without (no-DS) and with (DS) dynamic shortcuts for 199 \textit{original} tests (left) and 156 \textit{abstracted} tests (right)}
  \label{fig:precision}
  \vspace*{-1.5em}
\end{figure}

@@

Figure~\ref{fig:precision} depicts the comparison of the analysis
precision between no-DS and DS.  The $x$-axis and the $y$-axis denote
the number of failed assertions produced by no-DS and DS, respectively;
\inred{each circle denotes each test in heatmap form. The darker the circle is, the more tests it indicates.} The top line
denotes the y=x line, and the bottom solid line denotes the average improvement.
For 199 original tests that are analyzable by both analyzers,
Figure~\ref{fig:precision}(left) shows that dynamic shortcuts
\inred{completely removed the failed assertions for 24 tests, reducing the nuber of failed assertions by 92.79\% on average}.
For 156 abstracted tests that are analyzable by both analyzers,
Figure~\ref{fig:precision}(right) shows that dynamic shortcuts successfully cut down
the number of failed asserions by 12.31\% on average.
Thus, on average, dynamic shortcuts removed analysis of 92.79\% and 12.31\% failed assertions
for original and abstracted tests, respectively.

>>>>

\begin{figure}[t]
  \begin{subfigure}[t]{0.23\textwidth}
    \includegraphics[width=\linewidth]{img/conc-precision}
    \vspace*{-1.5em}
    \caption{199 \textit{original} tests}
    \label{fig:conc-precision}
  \end{subfigure}
  \begin{subfigure}[t]{0.23\textwidth}
    \includegraphics[width=\linewidth]{img/abs-precision}
    \vspace*{-1.5em}
    \caption{156 \textit{abstracted} tests}
    \label{fig:abs-precision}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Failed assertions of analysis without (no-DS) and with (DS) dynamic shortcuts}
  \label{fig:precision}
  \vspace*{-1.5em}
\end{figure}

@@

Figure~\ref{fig:precision} depicts the comparison of the analysis
precision between no-DS and DS.  The $x$-axis and the $y$-axis denote
the number of failed assertions produced by no-DS and DS, respectively;
\inred{each circle denotes each test in heatmap form. The darker the circle is, the more tests it indicates.} The top line
denotes the y=x line, and the bottom solid line denotes the average improvement.
For 199 original tests that are analyzable by both analyzers,
Figure~\ref{fig:conc-precision} shows that dynamic shortcuts
\inred{completely removed the failed assertions for 24 tests, reducing the nuber of failed assertions by 92.79\% on average}.
For 156 abstracted tests that are analyzable by both analyzers,
Figure~\ref{fig:abs-precision} shows that dynamic shortcuts successfully cut down
the number of failed asserions by 12.31\% on average.
Thus, on average, dynamic shortcuts removed analysis of 92.79\% and 12.31\% failed assertions
for original and abstracted tests, respectively.
